Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2017-12-19 eurocg/paper.tex
edits from meeting

\section{Definitions}

@@

\section{Two Polynomial Cases}
\subsection{Trees}
\fabian{Algorithm running in $O(kn)$ where $ k $ is the max degree of the tree.}

\subsection{Cacti of Degree Three}
\fabian{Algorithm running in $ O(kn) $.}

>>>>

Martin

\begin{itemize}
	\item motivation
	\item related work
	\item contribution
\end{itemize}

\section{Preliminaries}

Fabian

\begin{itemize}
	\item basic definitions and notation
	\item segment intersection graph
	\item alle planaren Graphen können auftreten (insbes. Bäume und Kakteen)
\end{itemize}

Input: $k$-plane graph drawing $\Gamma$ of a graph $G$ with edge set $S={s_1, \dots, s_m}$ (set of segments)

Intersection graph $C=(V,E)$ with $V=S$ and edges if two segments intersect

Consider maximum degree of $C$ -- here mostly 3.

@@

Soeren?

\section{Two Polynomial Cases}

\begin{itemize}
	\item dynamic programming
	\item table entries $T_i(s)$ for $i = 1, \dots, \deg(s)$
	\item $i$ corresponds to increasing stub lengths
	\item stub lengths $l_i(s)$ for $i = 1, \dots, \deg(s)$ (not the pair of stubs)
\end{itemize}

\subsection{Trees}
\fabian{Algorithm running in $O(kn)$ where $ k $ is the max degree of the tree + intersection graph bauen.}

Birgit

\begin{itemize}
	\item segment $s$ with $d$ children $u_1, \dots, u_{d}$ and parent $p(s) = p$.
	\item Assume children are sorted by their intersection points on $s$, i.e., $u_1$ produces stub length $l_1$ etc.
	\item for stub length relating to parent use offset from next longer stub length
\end{itemize}

\subsection{Cacti (of Degree Three)}
\fabian{Algorithm running in $ O(kn) $ + intersection graph bauen.}

\begin{itemize}
	\item seems to work for all cactus graphs
\end{itemize}
